% This example An LaTeX document showing how to use the l3proj class to
% write your report. Use pdflatex and bibtex to process the file, creating 
% a PDF file as output (there is no need to use dvips when using pdflatex).

% Modified 

\documentclass{l3proj}
\usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\begin{document}
\title{Project Title}
\author{Michael Kilian -- 1003819K \\
        Tony Lau -- 1102266L\\
        Dan Tomosoiu --1102486T \\
        Hector Grebbell -- 1007414G \\
        Peeranat Fupongsiripan -- 2056647F}
\date{19 March 2013}
\maketitle

\begin{abstract}
It is acknowledged that the cost of 
running evacuation drills in public environments is relatively high both in time and money. This is because very often, the 
evacuation drills have to be run at night where the chosen environment is not in service and consequently additional payments for 
equipment, hiring evacuees and fire consultants are needed.
There are also some types of evacuation that cannot be drilled both safely and accurately such as a large fire.
An evacuation simulator is a possible solution to these problems which uses human behaviour in an evacuation environment 
to predict the egress of a population. This project involves producing a three-dimensional visualised 
evacuation simulator of The Tall Ship at Riverside, Glasgow. Psychology of mass emergency evacuation behaviour and crowd patterns are applied in 
order to best determine how people will react in an evacuation situation. Furthermore, several pathfinding algorithms 
are studied to ascertain their relative suitability for the project.
The implementation side of this project 
involves the modelling of the chosen environment in 3D visualisation and simulating an evacuation on this model.
By combining these, the evacuation simulator can be more realistic.
\end{abstract}

\educationalconsent
\tableofcontents
%==============================================================================
\chapter{Introduction}
\label{introduction}

\input{../Intro/final_individual_writing}
\input{../Intro/Organisation}

%==============================================================================

\chapter{Team Structure \& Development Process}
\label{organisations}

\input{../Intro/Organisation}

%==============================================================================

\chapter{Requirements}
\label{requirements}
\input{../Requirements/team_project_requirement}

%==============================================================================
\chapter{Research}
\label{research}

\input{../Research/behaviourResearch}
\input{../Hector/SelectionofTools/selectionOfTools} %not complete

%Requirements (chapter on its own?)

%==============================================================================
\chapter{Design}
\label{design}

\input{../Design/PopulationAndGoalDesign}
\input{../Dan/testsize_importandnavmesh} %not complete

%==============================================================================
\chapter{Implementation}
\label{implementation}

\input{../Implementation/behaviourImplementationtest}
\input{../Hector/GUIDesignandImplementation/testsize_gui_dandi} %not complete

%==============================================================================
\chapter{Evaluation}
\label{evaluation}

\input{../MockEvacuationsAndWhyTheyDidntHappen}
\input{../Evaluation/guievaluation} %not complete

%==============================================================================
\chapter{Conclusion}
\label{conclusion}

\section{Requirements Acheived}
\input{../SummaryOfRequirementsAcheived.tex}}

\input{"../Hector/Future Work/futurework"}

\section{Summary}
In conclusion, the majority of the project's aims were achieved successfully.
However, there is the potential for significant future work to vastly improve the functionality the system provides.
It is hoped that the project will provide an extensible and flexible foundation for future development efforts.

\section{Contributions}
\label{contributions}

\begin{itemize}
\item{\textbf{Michael Kilian:} Quality assuror. Member of Implementation Team. Responsible for research into individual behaviour and corresponding design and implementation. Tester/Debugger. Wrote sections on behaviour research, Population package design, behavioural algorithms, process model and prototyping and team structure.}
\item{\textbf{Tony Lau:} }
\item{\textbf{Dan Tomosoiu: } Configuration Manager. Member of Implementation Team. Responsible for research into agent navigation and corresponding design and implementation. Tester/Debugger. Wrote sections on navigation structures design and implementation.}
\item{\textbf{Hector Grebbell: }}
\item{\textbf{Peeranat Fupongsiripan: }}
\end{itemize}

%==============================================================================
\clearpage
\appendix
\pagenumbering{roman}
%==============================================================================


\chapter{Prototypes and Problems Encountered}
\input{../PrototypeAndProblems}

\chapter{Think Aloud Evaluation Participant Notes}
\input{../Evaluation/appendix}


%==============================================================================
\chapter{Glossary}
\input{../Glossary}


%==============================================================================




\bibliographystyle{unsrt}
\bibliography{teamL_dissertation_2013}
\end{document}
